### 2017-04-23 paper.tex
Got half way through basic bound proof

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{color}

@@

\section*{Theorem 1}
If given a perceptron with known starting parameter $w_0$, desired parameter $w^*$, and unknown learning rate $\eta \in [\alpha , \beta]$ for given $\epsilon > 0$, we can guarantee $\eta \in [\alpha', \beta']$ such that $\beta' - \alpha' \leq \epsilon$ using $1 + \lceil \log_2(\frac{\beta - \alpha}{\epsilon})\rceil$

@@

\color{red}
Assume we now $w_1$
and $\eta_{min} \leq \eta \leq \eta_{max}$

and there is an $(x_2,y_2)$ such that $y_2 = 1$ and agrees with $w^*$ and not $w_1$. For some $c$ similar to orignal proof
let 
$$
x_2 = \frac{cw^* - w_1}{\beta}
$$

note 
$$
\frac{\alpha}{\alpha + \beta - \alpha}\leq \frac{\eta}{\beta}  \leq 1
$$

so
$$
w_1 + \eta x_2 = cw^* - \epsilon
$$
where
$
0 \leq \epsilon \leq (cw* - w_1) * \frac{\beta - \alpha}{\alpha + \beta - \alpha}  \leq \frac{\beta - \alpha}{\eta_{min} + \beta - \alpha} \leq \frac{\beta - \alpha}{\eta_{min}}
$

\color{red}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{color}
\usepackage{parskip}

\setlength{\parskip}{5pt}
\setlength{\parindent}{0pt}

@@

\section*{Theorem 1}
If given a perceptron with known starting parameter $w_0$, desired parameter $w^*$, and unknown learning rate $\eta \in [\alpha , \beta]$ for given $\epsilon > 0$, we can guarantee $\eta \in [\alpha', \beta']$ such that $\beta' - \alpha' \leq \epsilon$ using $1 + \lceil \log_2(\frac{\beta - \alpha}{\epsilon})\rceil$ examples.=

@@

Assume $w_0$ is known and $\eta \in [\eta_{\min} , \eta_{\max}] $ such that 
$0 < \eta_{\min} < \eta_{\max} < \infty$

Assume WLOG $\lVert w^* \rVert = 1$.

Pick $(x_1,y_1)$ such that $y_1 = -1$, $\lVert x_1 \rVert = \frac{2 \lVert w_0 \rVert}{\epsilon \eta_{\min}}$

\color{red}
Note when i say $y_1 = 1$, that implies that it agrees with $w^*$. And I'm pretty 
sure the above statement is valid. I think such an $x,y$ pair will always exist if
$w_0$ disagrees with $w^*$.
\color{black}

Then use the method from Theorem 1 to get a bound on $\eta$ such that $\eta \in [\alpha , \beta]$ and $\beta - \alpha <= ?$

Then let $x_2 = \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2}w^* + x_1$.
It should be clear that then $y_2 = 1$

Then realize that
$w_1 = w_0 - \eta x_1$

So
$$
y_2 \langle w_1, x_2 \rangle  = \bigg\langle \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha) /2} w^* + x_1 , w_0 - \eta x_1 \bigg\rangle
$$
$$
= \bigg\langle \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha) /2} w^* + x_1 , w_0  \bigg\rangle - \eta \lVert x_1 \rVert^2
$$
$$
\leq \bigg( \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha) /2} \lVert w^* \rVert + \lVert x_1 \rVert \bigg ) \lVert w_0 \rVert - \eta \lVert x_1 \rVert^2
$$
$$
= \frac{4 \lVert w_0 \rVert^2}{\epsilon (\beta + \alpha)/2} - \eta \frac{4 \lVert w_0 \rVert^2}{\epsilon^2 \eta_{\min}^2}
$$
$$
\leq \frac{4 \lVert w_0 \rVert^2}{\epsilon (\beta + \alpha)/2} -  \frac{4 \lVert w_0 \rVert^2}{\epsilon^2 \eta_{\min}}
$$
which is less than $0$ for $epsilon < 1$
